An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-26 uai2017/paper.tex
update new results
update paper

\begin{table}[t]
\caption{Average minibatch sizes ($\pm$ one standard deviation) on the Gaussian
mixture model. The averages are taken over 10 independent trials (3000 samples
each). \textbf{Daniel: Xinlei, can you add in one more decimal point for all the
numbers in this table, like I do in the Logistic Regression table?}}
% Daniel: this `small` command was carried over from the LR table which couldn't
% fit in a column. It's not needed here.
%\small 
\label{tab:gaussianres}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Method} & \textbf{Average of MB Sizes} \\
\hline \\
{\sc MHminibatch}   & $182\pm 12$ \\
{\sc AustereMH(c)}  & $13540\pm 1521$ \\
{\sc MHSubLhd}      & $65759\pm 3222$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{table}[t]
\caption{Gaussian Mixture Model Statistics \textbf{TODO Xinlei, please fix this
table.}}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric} & {\sc MHminibatch} & {\sc AustereMH} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & -1430.0 & -1578.9 & -1232.7 \\
Chi-Squared & 3313.9 & 3647.7 & 2444.1 \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

For large $n$, the per-bin distributions are approximated by Poissons with
parameter $\lambda_i=P_i n$. Given samples $\{\theta_1,\ldots,\theta_T\}$, let
$c_j$ denote the number of individual samples $\theta_i$ that fall in bin $j$
out of $N_{\rm bins}$ total. We have
\begin{equation}\label{eq:log_prob_poissons}
\log p(c_1, \ldots, c_{N_{\rm bins}} | P_1, \ldots, P_{N_{\rm bins}}) =
\sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)).
\end{equation}
Table~\ref{tab:poissons} shows the likelihoods. To facilitate interpretation we
perform significance tests using Chi-Squared distribution (also in
Table~\ref{tab:poissons}). Scores lie between~\citep{cutting_mh_2014}
and~\citep{icml2014c1_bardenet14}, but the variance of these values is high and
ordering changes depending on the range of samples generated. \textbf{Daniel:
Xinlei, one reviewer had a problem with this, and I agree. The easiest fix here
is to simply report standard deviation values. Also, we should emphasize that we
are not aiming to get the best score by this metric but simply something that
exhibits some form of ``correctness.''}

>>>>

\begin{table}[t]
\caption{Average minibatch sizes ($\pm$ one standard deviation) on the Gaussian
mixture model. The averages are taken over 10 independent trials (3000 samples
each). \textbf{Daniel: Xinlei, can you add in one more decimal point for all the
numbers in this table, like I do in the Logistic Regression table?}}
% Daniel: this `small` command was carried over from the LR table which couldn't
% fit in a column. It's not needed here.
%\small 
\label{tab:gaussianres}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Method} & \textbf{Average of MB Sizes} \\
\hline \\
{\sc MHminibatch}   & $182.3\pm 11.4$ \\
{\sc AustereMH(c)}  & $13540.5\pm 1521.4$ \\
{\sc MHSubLhd}      & $65758.9\pm 3222.6$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

\begin{table}[t]
\caption{Gaussian Mixture Model Statistics \textbf{TODO Xinlei, please fix this
table.}}
\small
\label{tab:poissons}
\vskip 0.15in
\begin{center}
\begin{tabular}{l l l l}
\textbf{Metric} & {\sc MHminibatch} & {\sc AustereMH} & {\sc MHSubLhd} \\
\hline
\T Equation~\ref{eq:log_prob_poissons} & $-1306.2 \pm 20.7$ & $-1619.6 \pm 25.3$ & $-1301.5 \pm 44.4$ \\
Chi-Squared & $5706.8 \pm 2271.5$ & $ 10501.3 \pm 2076.5$ & $ 3711.7 \pm 1182.4$ \\
\end{tabular}
\end{center}
\vskip -0.1in
\end{table}

@@

For large $n$, the per-bin distributions are approximated by Poissons with
parameter $\lambda_i=P_i n$. Given samples $\{\theta_1,\ldots,\theta_T\}$, let
$c_j$ denote the number of individual samples $\theta_i$ that fall in bin $j$
out of $N_{\rm bins}$ total. We have
\begin{equation}\label{eq:log_prob_poissons}
\log p(c_1, \ldots, c_{N_{\rm bins}} | P_1, \ldots, P_{N_{\rm bins}}) =
\sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)).
\end{equation}
Table~\ref{tab:poissons} shows the likelihoods. To facilitate interpretation we
perform significance tests using Chi-Squared distribution (also in
Table~\ref{tab:poissons}). The table provides the mean likelihood value and mean 
Chi-Squared test statistics value as well as their standard deviations.  Our likelihood values 
lies between~\citep{cutting_mh_2014} and~\citep{icml2014c1_bardenet14}, 
but the variance of their likelihood values are high and
ordering changes depending on the range of samples generated. It should be noted 
that we are not aiming at optimizing the likelihood values nor the Chi-Squared statistics.
We use these values to show the extent of correctness. \textbf{Daniel:
Xinlei, one reviewer had a problem with this, and I agree. The easiest fix here
is to simply report standard deviation values. Also, we should emphasize that we
are not aiming to get the best score by this metric but simply something that
exhibits some form of ``correctness.''}
